---
title: "shinypipe vignette"
author: "Karthik Rajendran"
date: "December, 2017"
output: 
  html_document:
    toc : true
    toc_float : true
    code_folding: hide
runtime: shiny
---

```{r Library, include=F}
rm(list = ls())

runWithoutInstall <- T
ifelse(runWithoutInstall,
       sapply(list.files(path = "../R/", pattern="*R", full.names = T), source),
       library(shinypipe))
```

### File upload 1

You can override the default selected values of *sep* and *header*

```{r }
ui.fread("file1")
data1 <- callModule(s.fread, "file1")
renderTable(head(data1()))
```

### File upload 2

Here, the user is not given the choice to select separator (by setting sep = NULL).
Instead, we can specify *sep* directly in the server function. 
The same may be achieved for header argument as well.
```{r }
ui.fread("file2", sep = NULL)
data2 <- callModule(s.fread, "file2", params = list(sep = ","))
renderTable(head(data2()))
```


### Formula editor

Upload a csv in the "File upload 1" case above to be able to create a formula. 

```{r}
renderUI({
  cols <- list(choices = names(data1()))
  ui.formula("fml", cols, cols, T)
})
```

#### Output formula
```{r}
fml <- callModule(s.formula, "fml")
renderPrint(fml())
```

Similar to the "File upload 2" example, the choice of whether to include intercept or not
can be hidden from the user by setting intercept to NULL.

### Sample formula usage

Perform a simple regression using the formula

```{r}
renderPrint(summary(lm(fml(), data1())))
```

### Using Params widget

```{r}
# TODO combine with formula
# ui.params("params")
# params <- callModule(s.params, "params")
```

