---
title: "Interactive regression and classification"
author: "Karthik Rajendran"
output: 
  flexdashboard::flex_dashboard:
    source_code: embed
    vertical_layout: scroll
    horizontal_layout: scroll
runtime: shiny
---

```{r Library, include=F}
rm(list = ls())
library(datasets)
library(data.table)
library(ggplot2)
library(DT)
library(caret)
library(flexdashboard)


runWithoutInstall <- F
ifelse(runWithoutInstall,
       sapply(list.files(path = "../R/", pattern="*R", full.names = T), source),
       library(shinypipe))

data(mtcars)
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
rv <- reactiveValues(table=as.data.table(mtcars), testIndices=NULL)


r.data <- reactive(rv$table[rv$testIndices])
r.data.test <- reactive(rv$table[!rv$testIndices])

```

Sidebar {.sidebar}
====================

```{r}
ui.fread("file", list(label="Alternative dataset (optional)"), sep = NULL, header=NULL)
r.dataF <- callModule(s.fread, "file", list(sep=",", header=T))
observe(rv$table <- r.dataF())

hr()
sliderInput("testPct", "% of test data", 5, 50, 25)
observeEvent(input$testPct, rv$testIndices <- createDataPartition(1:rv$table[,.N], p=(input$testPct/100), list=F))

hr()
renderUI({
  colsY <- list(choices = names(r.data()))
  colsX <- list(choices = names(r.data()), selected = names(r.data())[-1])
  ui.formula("form", colsY, colsX)
})
r.form <- callModule(s.formula, "form")
r.form.y <- callModule(s.formula.y, "form")

hr()
selectizeInput("model", "Model", names(getModelInfo()), selected = "svmRadial")

actionButton("run", "Train", width = "200px")

hr()
h4("Parameters") 
actionLink("help", "Click here for help")
hr()

observeEvent(input$help, showModal(modalDialog(
  "If left blank, a default training grid will be used, which can be used to later get an idea of suitable ranges. Otherwise, each parameter can either be a value or a range specified by any expression that evaluates to be a vector (like 1:4, c(1,2,5), seq(1,40,3) in case of a numeric field).  The tuning grid is shown in the Train tab. Make sure it's correct before you click on Train.",
  title = "Help", easyClose = T)))

model.params <- reactive(getModelInfo(input$model)[[input$model]]$parameter)

renderUI(ui.caretModel("model", model.params))
r.model1Params <- callModule(s.caretModel, "model", reactive(model.params()$parameter))

hr()

```


```{r Reactives}
r.modelInfo <- reactive(getModelInfo(input$model, F)[[input$model]])
```

Data
=====
### Data used
```{r}
renderDataTable(r.data())
```

### Notes
* In the default cars dataset, cyl and vs columns are factor variables that can be used with classification algorithms.

* Note that not all models may actually train when you click "Run" in the hosted version as not all libraries may be installed. If the document is run locally, packages can be installed as necessary. For the demo, choose functions like lm, svm\* and rvm\*.)

* Click on tabs on the top of the page to navigate to see the tuning grid created as you change the parameters, and 
control caret::train parameters. Hit run once you have the tuning grid you want.

Model
=======
### Selected Model Info
```{r}
getInfoTableFromObj <- function (model, info){
  data.table(Name=model,
             Description=paste(info$label, collapse=", "),
             Type=paste(info$type, collapse=", "),
             Library.Dependencies=paste(info$library, collapse=", "),
             Tags=paste(info$tags, collapse=", "))
}

renderTable(getInfoTableFromObj(input$model, r.modelInfo()))
```

### Model Browser (this info has been cached and could be out-of-date)
```{r}
# r.modelBrowser <- reactive({
#   m <- names(getModelInfo())
#   dt <- rbindlist(lapply(1:length(m), function(i) { getInfoTableFromObj(m[i], getModelInfo(m[i], F)[[m[i]]])}))
# })
load("caret_modelBrowser.RData")
renderDataTable(datatable(t.modelBrowser, filter = "top"))
```

Train
=========
### TuneGrid
```{r}
r.tuneGrid <- reactive(expand.grid(r.model1Params()))
renderDataTable(r.tuneGrid())
```

### List to override train parameters (See ?caret::train) {data-height="130px"}
```{r}
textAreaInput("trainList", NULL, width = '700px', height = "100px",
              value = "list()")
```

### List to override default train control (See ?caret::trainControl) {data-height="130px"}
```{r}
textAreaInput("trainControlList", NULL, width = '700px', height = "100px", 
              value = "list(method = 'cv', number = 3)")

r.trainParams <- reactive({
  input$run
  as.list(eval(parse(text = isolate(input$trainList))))
})

r.trainControl <- reactive({
  input$run
  do.call(trainControl, eval(parse(text = isolate(input$trainControlList))))
})
```

### Note: train may not work for all models in the hosted instance. Download locally and install necessary package to run these models.
```{r}
r.train <- reactive({
  input$run
  params <- isolate(r.trainParams()) 
  
  params$form <- r.form()
  params$data <- isolate(r.data())
  params$method <- isolate(input$model)
  params$trControl <- isolate(r.trainControl())

  grid <- isolate(r.tuneGrid())
  if (!is.null(grid) && nrow(grid) > 0)
    params$tuneGrid <- grid

  do.call(caret:::train.formula, params)
})

renderPrint(r.train())
```

Results
========
### Plot 
```{r}
fillRow(actionButton("renderPlotBtn", "Update"),
        textInput("renderPlotCmd", NULL, "plot(r.train())", width = "100%"),
        flex= c(NA,1), height ="50px")
```

### 
```{r}
renderPlot({
  input$renderPlotBtn
  eval(parse(text = isolate(input$renderPlotCmd)))
})
```

### Print 
```{r}
fillRow(actionButton("renderPrintBtn", "Update"),
        textInput("renderPrintCmd", NULL, "r.train()$finalModel", width = "100%"),
        flex= c(NA,1), height ="50px")
```

### 
```{r}
renderPrint({
  input$renderPrintBtn
  eval(parse(text = isolate(input$renderPrintCmd)))
})
```

Test
========

Column
-------

### 
```{r}
r.pred <- reactive({
  obs <- r.data.test()[, get(r.form.y())]
  pred <- predict(r.train(), r.data.test())
  data.table(obs = obs, pred = pred)
})

renderDataTable(r.pred())
```

Column
-------
```{r}
r.summary <- reactive(defaultSummary(r.pred()))
metric <- function(m, s) ifelse(m %in% names(s), formatC(s[[m]], digits = 4), "-")
```

### RMSE
```{r}
renderValueBox(metric("RMSE", r.summary()))
```

### Rsquared
```{r}
renderValueBox(metric("Rsquared", r.summary()))
```

### MAE
```{r}
renderValueBox(metric("MAE", r.summary()))
```

### Accuracy
```{r}
renderValueBox(metric("Accuracy", r.summary()))
```

### Kappa 
```{r} 
renderValueBox(metric("Kappa", r.summary()))
```
